---
title: "Peloton"
author: "Jack Cao"
date: "3/15/2023"
output: html_document
---

# set up
```{r}

# packages needed
library(tidyverse)   # for wrangling (e.g., dplyr) and visualization (ggplot2)
library(lubridate)   # for working with dates and timestamps
library(here)        # for setting the working directory since data is a .csv on local drive

# set set working directory
here::here()

# load data
workouts <- readr::read_csv("spa_cfx_tht_v2.csv")

# view data
utils::head(workouts)

```

# data cleaning
```{r}

workouts <- workouts %>% 
  
  # remove first column, which is the index from .csv
  dplyr::select(-1) %>%
  
  # reformat some columns
  dplyr::mutate(
    
    # workout_start_time as a timestamp
    workout_start_time = lubridate::as_datetime(workout_start_time),
    
    # fitness_discipline and class_type as factors
      # relatively few unique values compared to number of rows
    fitness_discipline =  base::factor(x = fitness_discipline),
    class_type = base::factor(x = class_type)
  
  )

```

# investigate NAs
```{r}

workouts %>% 
  dplyr::filter(is.na(class_length))

# rows with missing values are all cycling workouts; no class_type
# perhaps free/unstructured rides?

```


# add additional columns: data wrangling
```{r}

# part 1: additional information about each workout
workouts <- workouts %>%
  
  dplyr::mutate(
    
    # percent of the class completed; NA for free rides without a class length
    pct_of_class_completed = workout_length_minutes / class_length,
    
    # whether class was finished (1) or not (0)
    workout_finished = dplyr::case_when(
      pct_of_class_completed >= 1 ~ 1,
      TRUE ~ 0
    ),
    
    # time the workout ended: convert workout length in minutes to rounded seconds and add to workout start time
    workout_end_time = workout_start_time + lubridate::seconds(round(workout_length_minutes * 60, 0))
  
  )

# part 2: within each user for each workout, information about the previous and next workout
workouts <- workouts %>% 
  
  # reorder rows for previous workout information
  dplyr::arrange(
    user_id, workout_start_time
  ) %>%
  
  # next fields are specific to each user
  dplyr::group_by(user_id) %>%
  
  dplyr::mutate(
    
    # within each user, the discipline of the previous class
    previous_fitness_discipline = dplyr::lag(fitness_discipline, n = 1),
    
    # within each user, the previous class type
    previous_class_type = dplyr::lag(class_type, n = 1),
    
    # within each user, whether the previous class was finished
    previous_workout_finished = dplyr::lag(workout_finished, n = 1),

    # within each user, the start time of the previous workout
    previous_workout_start_time = dplyr::lag(workout_start_time, n = 1),
    
    # within each user, the end time of the previous workout
    previous_workout_end_time = dplyr::lag(workout_end_time, n = 1),
    
    
    # within each user, the discipline of the next class
    next_fitness_discipline = dplyr::lead(fitness_discipline, n = 1),
    
    # within each user, the next class type
    next_class_type = dplyr::lead(class_type, n = 1),
    
    # within each user, whether the next class was finished
    next_workout_finished = dplyr::lead(workout_finished, n = 1),

    # within each user, the start time of the next workout
    next_workout_start_time = dplyr::lead(workout_start_time, n = 1),
    
    # within each user, the end time of the next workout
    next_workout_end_time = dplyr::lead(workout_end_time, n = 1)
    
  ) %>%
  
  # ungroup for performance improvement
  dplyr::ungroup()

# part 3: within each user, how many minutes passed between previous workout's end time and the current workout's start time
workouts <- workouts %>%
  dplyr::mutate(
    
    num_minutes_btw_prev_and_current_workout = 
      lubridate::interval(previous_workout_end_time, workout_start_time) / lubridate::minutes(1),
    
    num_minutes_btw_current_and_next_workout = 
      lubridate::interval(workout_end_time, next_workout_start_time) / lubridate::minutes(1),

  )

# part 4: flag if each workout occurred after a completed cycling workout
workouts <- workouts %>%
  
  # whether workout occurred after a completed cycling workout (1) or not (0)
  dplyr::mutate(
    occurred_after_completed_cycling = dplyr::case_when(
      previous_fitness_discipline == "Cycling" & previous_workout_finished == 1 ~ 1, 
      TRUE ~ 0
    )
  )

# part 5: additional time information
workouts <- workouts %>%
  
  dplyr::mutate(
    
    # whether workout started on Mon, Tue, Wed, etc.
    day_of_week = lubridate::wday(workout_start_time, label = TRUE),
    
    # whether workout started on a weekend (1) or not (0)
    is_weekend = dplyr::case_when(
      day_of_week == "Sat" | day_of_week == "Sun" ~ 1,
      TRUE ~ 0
    ),
    
    # hour of the workout started
    hour_of_day = lubridate::hour(workout_start_time)
  ) 

```

# investigate negative num_minutes_btw_prev_and_current_workout
```{r}

workouts %>% 
  dplyr::count(
    ifelse(num_minutes_btw_prev_and_current_workout < 0,
           1,
           0
          )
    )

# users on multiple hardware devices?
# single user id but multiple human users?

```

# Slide 4: Users began over 60% of their non-cycling workouts after finishing a cycling workout
```{r}

workouts %>%
  
  # non-cycling workouts only
  dplyr::filter(
    fitness_discipline != "Cycling"
    ) %>%
  
  # only workouts with a positive minutes duration between previous and current
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%

  # how many non-cycling workouts occurred after a completed cycling workout
  dplyr::group_by(fitness_discipline, occurred_after_completed_cycling) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>% 
  
  # to make pretty for visualization
    # normalize to 100% for each non-cycling discipline
  dplyr::ungroup() %>%
  dplyr::group_by(fitness_discipline) %>%
  dplyr::mutate(total_workouts_started = base::sum(num_workouts_started), 
                pct = num_workouts_started / total_workouts_started) %>%
  
    # make pretty labels
  dplyr::mutate(
    fitness_discipline = base::factor(
      x = fitness_discipline, 
      levels = rev(c("Stretching", "Strength", "Yoga", "Meditation", "Cardio")),
      labels = rev(c("Stretching\n20,678 workouts started", "Strength\n30,465 workouts started",
                     "Yoga\n2,117 workouts started", "Meditation\n390 workouts started",
                     "Cardio\n155 workouts started"))
    ), 
    occurred_after_completed_cycling = base::factor(
      x = occurred_after_completed_cycling, 
      levels = c(0, 1), 
      labels = c("No", "Yes")
    )
  ) %>%
  
  # visualize
  ggplot(mapping = aes(x = fitness_discipline, y = pct, fill = occurred_after_completed_cycling)) + 
  geom_col(width = 0.5) + 
  geom_text(mapping = aes(label = scales::comma(num_workouts_started)), position = position_stack(vjust = 0.5)) + 
  coord_flip() + 
  scale_y_continuous(position = "right", labels = scales::percent_format(), breaks = seq(0, 1, 0.2)) + 
  labs(x = NULL, y = NULL, 
       fill = "Users started the\nnon-cycling workout\nafter they had\nfinished a cycling workout") + 
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank()) + 
  geom_hline(
    yintercept = 32470 / 53805,    # weighted average
    linetype = "dotted", 
    lwd = 1.5
  ) 
  
  

```

# Slide 5: Out of the non-cyclingw orkouts that began after a finished cycling workout, over 80% began within 10 minutes of the cycling workout's end.
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # reorder to make visualization prettier
  dplyr::mutate(
    fitness_discipline = base::factor(x = fitness_discipline, 
                                      levels = c("Stretching", "Strength", 
                                                 "Meditation", "Yoga", "Cardio"))
  ) %>% 
  
  # visualize
    # one line for each non-cycling discipline
  ggplot(mapping = aes(x = num_minutes_btw_prev_and_current_workout, color = fitness_discipline)) + 
  stat_ecdf() + 
    # add line for overall non-cycling
  stat_ecdf(
    data = workouts %>% 
      dplyr::filter(fitness_discipline != "Cycling") %>% 
      dplyr::filter(occurred_after_completed_cycling == 1) %>% 
      dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0),
    color = "black", lwd = 2
  ) + 
  scale_y_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format()) + 
  scale_x_continuous(breaks = seq(0, 20, 2)) + 
  coord_cartesian(xlim = c(0, 20), ylim = c(0, 1)) + 
  labs(x = "\nNumber of minutes between\nend of completed cycling workout\nand start of non-cycling workout", y = NULL, 
       color = "Non-cycling\nworkout") +
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank()) 

```

# Slide 7: Out of the non-cycling workouts that users started within 10 minutes of finishing a cycling workout, more than 70% were finished by users.
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # within 10 min
  dplyr::filter(num_minutes_btw_prev_and_current_workout <= 10) %>%
  
  # for each non-cycling workout, completion rate
  dplyr::group_by(class_type) %>%
  dplyr::summarise(num_workouts_finished = base::sum(workout_finished), 
                   total_workouts = dplyr::n_distinct(workout_id), 
                   pct = num_workouts_finished / total_workouts) %>%
  
  # make pretty for visualizing
  dplyr::ungroup() %>%
  
  dplyr::mutate(
    x_axis_label = base::paste0(
      class_type, ": ", total_workouts, " workouts"
    )
  ) %>%
  
  ggplot(mapping = aes(x = reorder(x_axis_label, pct), y = pct, fill = pct)) + 
  geom_col(width = 0.5) + 
  coord_flip() + 
  scale_fill_viridis_c() + 
  geom_hline(yintercept = 18765 / 26172, linetype = "dashed") + 
  scale_y_continuous(
    breaks = seq(0, 1, 0.1), labels = scales::percent_format(), 
    position = "right"
  ) + 
  labs(x = "Non-cycling workouts\nstarted within 10 min\nof finished cycling workout\n", 
       y = "Percent finished\n") + 
  theme_bw() + 
  theme(legend.position = "none", 
        axis.text = element_text(color = "black"), 
        panel.grid = element_blank(), 
        panel.border = element_blank())
  

```


# Slide 8: Users show consistent preferences for the type of non-cycling workout regardless of what cycling workout they completed.
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # within 10 min
  dplyr::filter(num_minutes_btw_prev_and_current_workout <= 10) %>% 
  
  # 
  dplyr::group_by(previous_class_type, class_type) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>%
  

  
  # normalize
  dplyr::ungroup() %>%
  dplyr::group_by(previous_class_type) %>%
  dplyr::mutate(
    total_cycling = base::sum(num_workouts_started),
    pct = num_workouts_started / total_cycling
  ) %>%

  # visualize
  ggplot(mapping = aes(x = previous_class_type, y = class_type, fill = pct)) + 
  geom_tile(color = "white", size = 0.5) + 
  scale_fill_viridis_c(labels = scales::percent_format()) + 
  labs(x = "Previous completed cycling class type", 
       y = "Next started non-cyclcing workout", 
       fill = "Within each\ncycling class type (column),\npercent of\nnon-cycling workouts\nthat began within 10 minutes") + 
  theme_bw() + 
  theme(
    axis.text = element_text(color = "black"),
    panel.grid = element_blank(), 
    #panel.border = element_blank(),
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  )

```

# Slide 10: Users tended to supplement their cycling workouts with strength and stretching workouts in the afternoons and evenings. Other non-cycling workouts were less common throughout the week.

```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # started within 10 minutes
  dplyr::filter(num_minutes_btw_prev_and_current_workout < 10) %>%

  # create new column for date_of for visual aesthetics
  dplyr::mutate(
    date_of = lubridate::date(workout_start_time), 
    date_of_label = paste0(date_of, ": ", day_of_week)
  ) %>% 
  
  # number started for these cuts
  dplyr::group_by(
    date_of_label, hour_of_day, fitness_discipline,
  ) %>%
  dplyr::summarise(
    num_workouts_started = dplyr::n_distinct(workout_id)
  ) %>%
  
  ggplot(
    mapping = aes(x = hour_of_day, y = num_workouts_started, color = fitness_discipline)
  ) + 
  facet_wrap(~date_of_label, nrow = 2) + 
  geom_line(lwd = 1.5, alpha = 0.5) + 
  labs(x = "Hour of the day", 
       title = "Number of non-cycling workouts\nstarted within 10 minutes of a finished cycling workout", subtitle = "On each day (panels) and cut by discipline (colors)", 
       y = NULL, fill = NULL, color = NULL) + 
  coord_cartesian(xlim = c(0, 24)) + 
  scale_x_continuous(breaks = seq(0, 24, 3)) + 
  theme_bw() + 
  theme(
    axis.text = element_text(color = "black"), 
    panel.grid.minor = element_blank()
  )






```


# Slide 11: After a completed cycling workout, there are upticks in non-cycling workouts at 12-15 hours and 24 hours.
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # reorder to make visualization prettier
  dplyr::mutate(
    fitness_discipline = base::factor(x = fitness_discipline, 
                                      levels = c("Stretching", "Strength", 
                                                 "Meditation", "Yoga", "Cardio"))
  ) %>% 
  
  # visualize
    # one line for each non-cycling discipline
  ggplot(mapping = aes(x = num_minutes_btw_prev_and_current_workout / 60, color = fitness_discipline)) + 
  stat_ecdf() + 
    # add line for overall non-cycling
  stat_ecdf(
    data = workouts %>% 
      dplyr::filter(fitness_discipline != "Cycling") %>% 
      dplyr::filter(occurred_after_completed_cycling == 1) %>% 
      dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0),
    color = "black", lwd = 2
  ) + 
  scale_y_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format()) + 
  scale_x_continuous(breaks = seq(0, 36, 3)) + 
  coord_cartesian(xlim = c(0, 36), ylim = c(0, 1)) + 
  labs(x = "\nNumber of hours between\nend of completed cycling workout\nand start of non-cycling workout", y = NULL, 
       color = "Non-cycling\nworkout") +
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank()) 

```
# Slide 13: As an adoption target, we should consider a 6% uplift in completed cycling workouts that are followed by a non-cycling workout within 10 minutes
 
```{r}

# 476,425 total workouts
nrow(workouts)

# 415,008 cycling workouts
workouts %>%
  dplyr::count(fitness_discipline)


  # calculate: 26,148 cycling workouts that are followed by non-cycling workout within 10 minutes
workouts %>%
  dplyr::filter(
    fitness_discipline == "Cycling"
      & workout_finished == 1
      & next_fitness_discipline != "Cycling"
      & num_minutes_btw_current_and_next_workout > 0 
      & num_minutes_btw_current_and_next_workout <= 10
    ) %>%
  nrow()

  # pull forward in time: 1,683: adoption target raw count
workouts %>%
  dplyr::filter(
    fitness_discipline == "Cycling"
      & workout_finished == 1
      & next_fitness_discipline != "Cycling"
      & num_minutes_btw_current_and_next_workout > 10
      & num_minutes_btw_current_and_next_workout <= 30
    ) %>%
  nrow()

  # 4,615: out of scope for queuing feature
workouts %>%
  dplyr::filter(
    fitness_discipline == "Cycling"
      & workout_finished == 1
      & next_fitness_discipline != "Cycling"
      & num_minutes_btw_current_and_next_workout > 30
    ) %>%
  nrow()


workouts %>%
  dplyr::filter(
    fitness_discipline == "Cycling"
      & workout_finished == 1
      & next_fitness_discipline != "Cycling"
      & num_minutes_btw_current_and_next_workout > 30
    ) %>%
  dplyr::pull(num_minutes_btw_current_and_next_workout) %>%
  median()

1362.267 / 60  # 22.7 hours --> 1 day later

```

# Slide 13: As an adoption target, we should consider a 6% uplift in completed cycling workouts that are followed by a non-cycling workout within 10 minutes
```{r}

tibble::tibble(
  time_to_start = c("< 10 min", "10 - 30 min", "> 30 min"), 
  num_workouts = c(26148, 1683, 4615)
) %>%
  dplyr::mutate(time_to_start = base::factor(time_to_start, 
                                             levels = c("< 10 min", "10 - 30 min", "> 30 min"))) %>% 
  ggplot(mapping = aes(x = time_to_start, y = num_workouts)) + 
  geom_col(width = 0.33) + 
  geom_text(mapping = aes(label = scales::comma(num_workouts)), 
            vjust = -1) + 
  labs(x = "\nTime between finishing the cycling workout and\nstarting the next non-cycling workout", 
       y = NULL, 
       title = "Number of finished cycling workouts that were followed by a non-cycling workout", 
       subtitle = "By the same user") + 
  coord_cartesian(ylim = c(0, 30000)) + 
  scale_y_continuous(labels = scales::comma_format(), 
                     breaks = seq(0, 30000, 5000)) +
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid = element_blank())
  

```

# Slide 15:
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(occurred_after_completed_cycling == 1) %>%

  # exclude workouts with negative time duration in between
  dplyr::filter(num_minutes_btw_prev_and_current_workout >= 0) %>%
  
  # where next fitness class was cycling
  dplyr::filter(
    next_fitness_discipline == "Cycling"
  ) %>%
  
  dplyr::pull(num_minutes_btw_current_and_next_workout) %>%
  stats::median()

# 1 day, 23.9 hours
1432.583 / 60

```


# Slide 16: no code, just conceptual

# on how many days was each user active?
```{r}

# across all users, avg user was active on 2.35 days out of 7
workouts %>%
  dplyr::group_by(user_id) %>%
  dplyr::summarise(
    num_days_active = dplyr::n_distinct(lubridate::date(workout_start_time))
  ) %>%
  dplyr::pull(num_days_active) %>%
  mean()



```

# on how many days were the cycling-non cycling users active?
```{r}

# identify those users
users_back_to_back <- workouts %>%
  dplyr::filter(
    fitness_discipline == "Cycling"
      & workout_finished == 1
      & next_fitness_discipline != "Cycling"
      & num_minutes_btw_current_and_next_workout > 0
      & num_minutes_btw_current_and_next_workout <= 10
    ) %>%
  dplyr::pull(user_id) %>%
  unique()

# how many days were they active?
workouts %>%
  dplyr::filter(
    user_id %in% users_back_to_back
  ) %>%
  dplyr::group_by(user_id) %>%
  dplyr::summarise(
    num_days_active = dplyr::n_distinct(lubridate::date(workout_start_time))
  ) %>%
  dplyr::pull(num_days_active) %>%
  mean()

# 3.40 days

```


# Appendix

# exploratory analysis: understand relationship between fitness_discipline and class_type
```{r}

workouts %>%
  dplyr::group_by(fitness_discipline, class_type) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>% 
  ggplot(mapping = aes(x = class_type, y = num_workouts)) + 
  facet_wrap(~fitness_discipline, scales = "free", nrow = 3) + 
  geom_col() + 
  coord_flip()

# fitness_discipline is the umbrella
# class_type are sub-categories within fitness_discipline

```

# exploratory analysis: number of workouts finsihed by class_type and fitness_discipline
same as above except fill colors to indicate how many finished vs. not
```{r}

workouts %>%
  dplyr::group_by(fitness_discipline, class_type, workout_finished) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>%
  ggplot(mapping = aes(x = class_type, y = num_workouts, fill = base::as.factor(workout_finished))) + 
  facet_wrap(~fitness_discipline, scales = "free", nrow = 3) + 
  geom_col() + 
  coord_flip() + 
  theme(
    legend.position = "top"
  )

```
# exploratory analysis: distribution of number of workouts started by day
```{r}

workouts %>%
  dplyr::mutate(
    workout_start_date = lubridate::as_date(workout_start_time)
  ) %>% 
  dplyr::group_by(workout_start_date, day_of_week) %>%
  dplyr::summarise(num_workouts_started = n_distinct(workout_id)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    day = base::paste0(workout_start_date, ", ", day_of_week), 
    pct_of_workouts_started = num_workouts_started / base::sum(num_workouts_started)
  ) %>%
  ggplot(mapping = aes(x = day, y = pct_of_workouts_started)) + 
  geom_col() + 
  coord_flip() + 
  scale_x_discrete(limits = rev) + 
  scale_y_continuous(labels = scales::percent_format())

# Sun is least busy day. Picks up on Mon and Tue. Decrease from Wed-Fri and picks up again on Sat.

```

# exploratory analysis: on each day, at what hour do workouts begin?
```{r}

workouts %>%
  dplyr::mutate(
    workout_start_date = lubridate::as_date(workout_start_time), 
    day = base::paste0(workout_start_date, ", ", day_of_week)
  ) %>%
  dplyr::group_by(day, hour_of_day) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>%
  ggplot(mapping = aes(x = hour_of_day, y = num_workouts_started)) + 
  facet_wrap(~day) + 
  geom_col()

```

# exploratory analysis: distribution of number of workouts started per user
```{r}

# right skewed distribution: >90% of users have 6 or fewer workouts during the week

workouts %>% 
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>% 
  dplyr::group_by(num_workouts_started) %>%
  dplyr::summarise(num_users = dplyr::n_distinct(user_id)) %>%
  dplyr::arrange(num_workouts_started) %>%
  dplyr::mutate(
    cum_pct_of_users = base::cumsum(num_users) / base::sum(num_users)
  ) %>% 
  ggplot(mapping = aes(x = num_workouts_started, y = cum_pct_of_users)) + 
  geom_point() + 
  geom_line() + 
  coord_cartesian(ylim = c(0, 1)) + 
  scale_y_continuous(labels = scales::percent_format(), 
                     breaks = seq(0, 1, 0.2))

# how to improve chart
# label 1 thru 6 and outliers above and below 400
# latter are perhaps single-user, multiple people

```

