---
title: "peloton_take_home"
author: "Jack Cao"
date: "3/11/2023"
output: html_document
---

# set up
```{r}

# packages needed
library(tidyverse)
library(here)

# set set working directory
here::here()

# load data
base::list.files()
workouts <- readr::read_csv("spa_cfx_tht_v2.csv")

# view data
utils::head(workouts)

```

# data cleaning
```{r}

workouts <- workouts %>% 
  
  # remove first column, which is the index from .csv
  dplyr::select(-1) %>%
  
  # reformat some columns
  dplyr::mutate(
    
    # workout_start_time as a timestamp
    workout_start_time = lubridate::as_datetime(workout_start_time),
    
    # fitness_discipline and class_type as factors
      # relatively few unique values compared to number of rows
    fitness_discipline =  base::factor(x = fitness_discipline),
    class_type = base::factor(x = class_type)
  
  )

```

# add additional columns
```{r}

# part 1: additional information about each workout
workouts <- workouts %>%
  
  dplyr::mutate(
    
    # percent of the class completed
    pct_of_class_completed = workout_length_minutes / class_length,
    
    # whether class was finished (1) or not (0)
    workout_finished = dplyr::case_when(
      pct_of_class_completed >= 1 ~ 1,
      TRUE ~ 0
    ),
    
    # time the workout ended: convert workout length in minutes to rounded seconds and add to workout start time
    workout_end_time = workout_start_time + lubridate::seconds(round(workout_length_minutes * 60, 0))
  
  )

# part 2: within each user for each workout, information about the previous workout
workouts <- workouts %>% 
  
  # reorder rows for previous workout information
  dplyr::arrange(
    user_id, workout_start_time
  ) %>%
  
  # next fields are specific to each user
  dplyr::group_by(user_id) %>%
  
  dplyr::mutate(
    
    # within each user, the discipline of the previous class
    previous_fitness_discipline = dplyr::lag(fitness_discipline, n = 1),
    
    # within each user, whether the previous class was finished
    previous_workout_finished = dplyr::lag(workout_finished, n = 1),
    
    # within each user, the end time of the previous workout
    previous_workout_end_time = dplyr::lag(workout_end_time, n = 1)
  )

# part 3: within each user, how many minutes passed between previous workout's end time and the current workout's start time
  # this takes a while
workouts <- workouts %>%
  dplyr::mutate(
    num_minutes_btw_prev_and_current_workout = 
      lubridate::interval(previous_workout_end_time, workout_start_time) / lubridate::minutes(1)
  )
  

```


```{r}

workouts %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    neg = dplyr::case_when(
      num_minutes_btw_prev_and_current_workout < 0 ~ 1,
      TRUE ~ 0
    )
  ) %>%
  dplyr::count(neg)

11092/nrow(workouts) ## 2% of workout

```


# how many workouts occur after a completed cycling workout by the same user?
```{r}

workouts %>%
  
  # non-cycling workouts
  dplyr::filter(fitness_discipline != "Cycling") %>% 
  
  # number of workouts started by what the previous work out was, whether it was finished, and the current workout discipline
  dplyr::group_by(previous_fitness_discipline, previous_workout_finished, fitness_discipline) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>%
  
  # flag for whether previous workout was a completed Cycling workout
  dplyr::ungroup() %>%
  dplyr::mutate(
    occurred_after_completed_cycling = dplyr::case_when(
      previous_fitness_discipline == "Cycling" & previous_workout_finished == 1 ~ 1, 
      TRUE ~ 0
    )
  ) %>%
  
  # counts and percent
  dplyr::group_by(occurred_after_completed_cycling, fitness_discipline) %>%
  dplyr::summarise(num_workouts_started = base::sum(num_workouts_started)) %>%
  dplyr::arrange(fitness_discipline, occurred_after_completed_cycling) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(fitness_discipline) %>%
  dplyr::mutate(total_workouts_started = base::sum(num_workouts_started), 
                pct = num_workouts_started / total_workouts_started) %>%
  
  # aesthetics for visualizing
  dplyr::mutate(
    fitness_discipline = base::factor(
      x = fitness_discipline, 
      levels = rev(c("Stretching", "Strength", "Yoga", "Meditation", "Cardio")),
      labels = rev(c("Stretching\n24,251 workouts started", "Strength\n33,647 workouts started",
                 "Yoga\n2,807 workouts started", "Meditation\n455 workouts started",
                 "Cardio\n157 workouts started"))
    ), 
    occurred_after_completed_cycling = base::factor(
      x = occurred_after_completed_cycling, 
      levels = c(0, 1), 
      labels = c("No", "Yes")
    )
  ) %>% 
  
  # visualize
  ggplot(mapping = aes(x = fitness_discipline, y = pct, fill = occurred_after_completed_cycling)) + 
  geom_col(width = 0.5) + 
  geom_text(mapping = aes(label = scales::comma(num_workouts_started)), position = position_stack(vjust = 0.5)) + 
  coord_flip() + 
  scale_y_continuous(position = "right", labels = scales::percent_format(), breaks = seq(0, 1, 0.2)) + 
  labs(x = NULL, y = NULL, 
       fill = "Users started the\nnon-cycling workout\nafter they had\nfinished a cycling workout") + 
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank()) + 
  geom_hline(
    yintercept = 35869 / 61317, 
    linetype = "dashed"
  ) 

```
# number of minutes started, cumulative distribution
```{r}

workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(previous_fitness_discipline == "Cycling" & previous_workout_finished == 1) %>%
  
  dplyr::mutate(
    fitness_discipline = base::factor(x = fitness_discipline, 
                                      levels = c("Stretching", "Strength", 
                                                 "Meditation", "Yoga", "Cardio"))
  ) %>% 
  
  ggplot(mapping = aes(x = num_minutes_btw_prev_and_current_workout, color = fitness_discipline)) + 
  stat_ecdf() + 
  #stat_ecdf(
   # data = workouts %>% 
    #  dplyr::filter(fitness_discipline != "Cycling") %>% 
     # dplyr::filter(previous_fitness_discipline == "Cycling" & previous_workout_finished == 1),
    #color = "black", lwd = 2
  #) + 
  scale_y_continuous(breaks = seq(0, 1, 0.1), labels = scales::percent_format()) + 
  #scale_x_continuous(breaks = seq(0, 10, 1)) + 
  coord_cartesian(xlim = c(0, 2500)) + 
  labs(x = "\nNumber of minutes between\nend of completed cycling workout\nand start of non-cycling workout", y = NULL, 
       color = "Non-cycling\nworkout") +
  theme_bw() + 
  theme(axis.text = element_text(color = "black"), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank()) 
  
  


```

# matrix view: granular view of class_type
```{r}

workouts <- workouts %>%
  dplyr::mutate(
    previous_class_type = dplyr::lag(class_type, n = 1)
  )

# 
workouts %>%
  
  # non-cycling workouts...
  dplyr::filter(fitness_discipline != "Cycling") %>%
  
  # ...that began after a completed a cycling class
  dplyr::filter(previous_fitness_discipline == "Cycling" & previous_workout_finished == 1) %>%
  
  # 
  dplyr::group_by(previous_class_type, class_type) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>%
  
  # normalize
  dplyr::ungroup() %>%
  dplyr::group_by(previous_class_type) %>%
  dplyr::mutate(
    total_cycling = base::sum(num_workouts_started),
    pct = num_workouts_started / total_cycling
  ) %>%

  # visualize
  ggplot(mapping = aes(x = previous_class_type, y = class_type, fill = pct)) + 
  geom_raster() + 
  scale_fill_viridis_c() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```



# other stuff below

# data cleaning 
```{r}

dat <- dat %>% 
  
  # remove first column, which is the index from .csv
  dplyr::select(-1) %>%
  
  # reformat some columns
  dplyr::mutate(
    
    # workout_start_time as a timestamp
    workout_start_time = lubridate::as_datetime(workout_start_time),
    
    # fitness_discipline and class_type as factors
      # relatively few unique values compared to number of rows
    fitness_discipline =  base::factor(x = fitness_discipline),
    class_type = base::factor(x = class_type)
  
  )

```


# add additional columns for potential cuts
```{r}

dat <- dat %>%
  
  # additional columns from workout_start_time
  dplyr::mutate(
    
    # whether workout started on Mon, Tue, Wed, etc.
    day_of_week = lubridate::wday(workout_start_time, label = TRUE),
    
    # whether workout started on a weekend (1) or not (0)
    is_weekend = dplyr::case_when(
      day_of_week == "Sat" | day_of_week == "Sun" ~ 1,
      TRUE ~ 0
    ),
    
    # hour of the workout started
    hour_of_day = lubridate::hour(workout_start_time)
    
  ) %>%
  
  # additional columns based on workout_length_minutes and class_length
  dplyr::mutate(
    
    # percent of the class completed
    pct_of_class_completed = workout_length_minutes / class_length,
    
    # whether class was finished (1) or not (0)
    workout_finished = dplyr::case_when(
      pct_of_class_completed >= 1 ~ 1,
      TRUE ~ 0
    )
  )


```


# exploratory analysis: understand relationship between fitness_discipline and class_type
```{r}

dat %>%
  dplyr::group_by(fitness_discipline, class_type) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>% 
  ggplot(mapping = aes(x = class_type, y = num_workouts)) + 
  facet_wrap(~fitness_discipline, scales = "free", nrow = 3) + 
  geom_col() + 
  coord_flip()

# fitness_discipline is the umbrella
# class_type are sub-categories within fitness_discipline

```


# exploratory analysis: number of workouts finsihed by class_type and fitness_discipline
same as above except fill colors to indicate how many finished vs. not
```{r}

dat %>%
  dplyr::group_by(fitness_discipline, class_type, workout_finished) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>%
  ggplot(mapping = aes(x = class_type, y = num_workouts, fill = base::as.factor(workout_finished))) + 
  facet_wrap(~fitness_discipline, scales = "free", nrow = 3) + 
  geom_col() + 
  coord_flip() + 
  theme(
    legend.position = "top"
  )

```


# exploratory analysis: percent of workouts finsihed by class_type and fitness_discipline
same as above except each bar is normalized to 100%
```{r}

dat %>%
  dplyr::group_by(fitness_discipline, class_type, workout_finished) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(fitness_discipline, class_type) %>%
  dplyr::mutate(pct_workouts = num_workouts / base::sum(num_workouts)) %>%
  
  # to zoom in on a particular fitness_discipline
  #dplyr::filter(fitness_discipline == "Cycling") %>% 
  
  ggplot(mapping = aes(x = class_type, y = pct_workouts, fill = base::as.factor(workout_finished))) + 
  facet_wrap(~fitness_discipline, scales = "free", nrow = 3) + 
  geom_col() + 
  coord_flip() + 
  theme(
    legend.position = "top"
  )

```



# exploratory analysis: distribution of number of workouts started by day
```{r}

dat %>%
  dplyr::mutate(
    workout_start_date = lubridate::as_date(workout_start_time)
  ) %>% 
  dplyr::group_by(workout_start_date, day_of_week) %>%
  dplyr::summarise(num_workouts_started = n_distinct(workout_id)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    day = base::paste0(workout_start_date, ", ", day_of_week), 
    pct_of_workouts_started = num_workouts_started / base::sum(num_workouts_started)
  ) %>%
  ggplot(mapping = aes(x = day, y = pct_of_workouts_started)) + 
  geom_col() + 
  coord_flip() + 
  scale_x_discrete(limits = rev) + 
  scale_y_continuous(labels = scales::percent_format())

# Sun is least busy day. Picks up on Mon and Tue. Decrease from Wed-Fri and picks up again on Sat.

```

# exploratory analysis: on each day, at what hour do workouts begin?
```{r}

dat %>%
  dplyr::mutate(
    workout_start_date = lubridate::as_date(workout_start_time), 
    day = base::paste0(workout_start_date, ", ", day_of_week)
  ) %>%
  dplyr::group_by(day, hour_of_day) %>%
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>%
  ggplot(mapping = aes(x = hour_of_day, y = num_workouts_started)) + 
  facet_wrap(~day) + 
  geom_col()

```




# exploratory analysis: distribution of number of workouts started per user
```{r}

# right skewed distribution: >90% of users have 6 or fewer workouts during the week

dat %>% 
  dplyr::group_by(user_id) %>% 
  dplyr::summarise(num_workouts_started = dplyr::n_distinct(workout_id)) %>% 
  dplyr::group_by(num_workouts_started) %>%
  dplyr::summarise(num_users = dplyr::n_distinct(user_id)) %>%
  dplyr::arrange(num_workouts_started) %>%
  dplyr::mutate(
    cum_pct_of_users = base::cumsum(num_users) / base::sum(num_users)
  ) %>% 
  ggplot(mapping = aes(x = num_workouts_started, y = cum_pct_of_users)) + 
  geom_point() + 
  geom_line() + 
  coord_cartesian(ylim = c(0, 1)) + 
  scale_y_continuous(labels = scales::percent_format(), 
                     breaks = seq(0, 1, 0.2))

# how to improve chart
# label 1 thru 6 and outliers above and below 400
# latter are probably single-user, multiple people

```

# for each user, how much time passed between each workout?
this works but takes a long time
```{r}

# for each user, the timestamp of their previous workout start
dat <- dat %>% 
  dplyr::arrange(user_id, workout_start_time) %>% 
  dplyr::group_by(user_id) %>% 
  dplyr::mutate(
    previous_workout_start_time = dplyr::lag(workout_start_time, n = 1)
  ) %>%
  dplyr::relocate(previous_workout_start_time, .after = workout_start_time) %>%
  dplyr::mutate(
    num_mins_since_last_workout_start = 
      lubridate::interval(previous_workout_start_time, workout_start_time) / 
        lubridate::minutes(1)
  ) %>%
  dplyr::relocate(num_mins_since_last_workout_start, .after = previous_workout_start_time)


head(dat)


```

# for each workout, what was the workout_end_time, irrespective of whether it was finished or not
```{r}

dat <- dat %>%
  dplyr::mutate(
    workout_end_time = workout_start_time + lubridate::seconds(round(workout_length_minutes * 60, 0))
  ) 

# relocate columns
dat <- dat %>%
  relocate(
    workout_length_minutes, .after = previous_workout_start_time
  ) %>%
  relocate(
   workout_end_time, .after =  workout_length_minutes
  )

```




# Q1: Should we explore building this feature? Dees the data support potential demand for it among our users?
* Solution 1: Queue up workout
* Solution 2: Recommend 2-4 classes

Approach/Considerations:
* If there's demand: we should see users doing multiple workouts relatively back to back. Look at the time duration between workouts.
* If there aren't users doing back to back workouts, that could indicate lack of demand or there is latent demand but there's too much friction to start second workout


## create user level table
user_id
num_total_workouts_started
num_cycling_workouts_started
num_noncyling_workouts_started
num_total_workouts_finished
num_cycling_workouts_finished
num_noncyling_workouts_finished

```{r}

users <- dat %>%
  
  dplyr::group_by(user_id) %>%
  
  dplyr::summarise(
    
    # total workouts started
    num_total_workouts_started = dplyr::n(),
    
    # cycling workouts started
    num_cycling_workouts_started = base::sum(
      ifelse(fitness_discipline == "Cycling", 1, 0)
    ),
    
    # non-cycling workouts started
    num_noncycling_workouts_started = base::sum(
      ifelse(fitness_discipline != "Cycling", 1, 0)
    ),
    
    # total workouts finished
    num_total_workouts_finished = base::sum(workout_finished),
    
    # cycling workouts finished
    num_cycling_workouts_finished = base::sum(
      ifelse(fitness_discipline == "Cycling" & workout_finished == 1, 1, 0)
    ),
    
    # non-cycling workouts finished
    num_noncycling_workouts_finished = base::sum(
      ifelse(fitness_discipline != "Cycling" & workout_finished == 1, 1, 0)
    )
    
  )

```

## check the user level table
```{r}

sum(users$num_total_workouts_started == users$num_cycling_workouts_started + users$num_noncycling_workouts_started) == nrow(users)

sum(users$num_total_workouts_finished == users$num_cycling_workouts_finished + users$num_noncycling_workouts_finished) == nrow(users)

sum(users$num_total_workouts_finished <= users$num_total_workouts_started) == nrow(users)



```

## top of the tree: all users
```{r}

length(unique(users$user_id))


```

## second level of tree: users who started 1+ cycling workout vs. not
```{r}

# users who started 1+ cycling workout: 154,056
users %>%
  dplyr::filter(
    num_cycling_workouts_started >= 1
  )

# users who didn't start 1+ cycling workout: 1,268
users %>%
  dplyr::filter(
    num_cycling_workouts_started == 0
  )

```

## third level of tree: break apart 154,056
```{r}

# users whose 1+ cycling workout started was their only workout started: 51,572
users %>%
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  dplyr::filter(
    num_total_workouts_started == 1 
  )

# users whose 1+ cycling workout started was one of multiple workouts started: 102,484
users %>%
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  dplyr::filter(
    num_total_workouts_started > 1 
  )


```
# tangent: break up the 51,572 users who just started 1 workout, which was a cycling workout
```{r}

users %>%
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  dplyr::filter(
    num_total_workouts_started == 1 
  ) %>%
  dplyr::group_by(num_cycling_workouts_finished) %>%
  dplyr::summarise(num_users = n_distinct(user_id))

```
## break up the 102,484: how many finished at least 1 cycling workout
```{r}

users %>%
  
  # started at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  
  # started multiple workouts
  dplyr::filter(
    num_total_workouts_started > 1 
  ) %>%
  
  dplyr::group_by(num_cycling_workouts_finished) %>%
  dplyr::summarise(n_users = dplyr::n_distinct(user_id)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    num_cycling_workouts_finished_bucket = dplyr::case_when(
      num_cycling_workouts_finished == 0 ~ "0",
      TRUE ~ "1+"
    )
  ) %>%
  dplyr::group_by(num_cycling_workouts_finished_bucket) %>%
  dplyr::summarise(n_users = base::sum(n_users))


```
# break up the 98,559 users
```{r}

users %>%
  
  # started at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  
  # started multiple workouts
  dplyr::filter(
    num_total_workouts_started > 1 
  ) %>%
  
  dplyr::filter(
    num_cycling_workouts_finished >= 1
  )

```
# of the 98,559 users: how many started non-cycling workouts?
```{r}

# 23,717
users %>%
  
  # started at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  
  # and started multiple workouts
  dplyr::filter(
    num_total_workouts_started > 1 
  ) %>%
  
  # and finished at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_finished >= 1
  ) %>%
  
  dplyr::filter(num_noncycling_workouts_started >= 1)
  
  


```


# of the 98,559 users: how many didn't start non-cycling workouts?
i.e., just cycling
```{r}

# 74,782
users %>%
  
  # started at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  
  # and started multiple workouts
  dplyr::filter(
    num_total_workouts_started > 1 
  ) %>%
  
  # and finished at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_finished >= 1
  ) %>%
  
  dplyr::filter(num_noncycling_workouts_started == 0)

```
# get to the point: sub-population to focus on
```{r}

users %>%
  dplyr::filter(
    num_cycling_workouts_finished >= 1 &      # users who finished 1+ cycling workouts
      num_noncycling_workouts_started >= 1    # and started 1+ non-cycling workouts
  )

```

# extract user_id of 23,717 to focus on
```{r}

user_id_finished_1plus_cycling_started_1plus_noncycling <- 
users %>%
  dplyr::filter(
    num_cycling_workouts_finished >= 1 &      # users who finished 1+ cycling workouts
      num_noncycling_workouts_started >= 1    # and started 1+ non-cycling workouts
  ) %>%
  dplyr::pull(user_id)

length(unique(user_id_finished_1plus_cycling_started_1plus_noncycling))

```

# just the population to focus on
```{r}

workout_subpop <- dat %>%
  dplyr::filter(user_id %in% user_id_finished_1plus_cycling_started_1plus_noncycling) %>%
  dplyr::select(
    user_id, workout_id, fitness_discipline, class_type,
    day_of_week, is_weekend, hour_of_day,
    workout_start_time, workout_length_minutes, workout_end_time, 
    class_length, pct_of_class_completed, workout_finished,
    previous_workout_start_time, num_mins_since_last_workout_start
  ) %>%
  dplyr::arrange(user_id, workout_start_time)


colnames(dat)
```

# relevant columns
```{r}

workout_subpop <- workout_subpop %>%
  dplyr::select(
    user_id, workout_id, fitness_discipline, class_type,
    workout_start_time, workout_length_minutes, class_length, pct_of_class_completed, workout_finished,
    workout_end_time 
  )

# flags to indicate within each user_id, was the previous workout a completed cycling class
workout_subpop <- workout_subpop %>%
  dplyr::group_by(user_id) %>%
  dplyr::mutate(
    previous_fitness_discipline = dplyr::lag(fitness_discipline, n = 1),
    previous_workout_finished = dplyr::lag(workout_finished,n = 1)
  )

# within each user_id, previous workout's end time
workout_subpop <- workout_subpop %>%
  dplyr::group_by(user_id) %>%
  dplyr::mutate(
    previous_workout_end_time = dplyr::lag(workout_end_time, n = 1)
  )

# how many minutes passed between previous workout's end time and the current workout's start time
workout_subpop <- workout_subpop %>%
  dplyr::mutate(
    num_minutes_between_previous_workout_end_and_current_workout_start = 
      lubridate::interval(previous_workout_end_time, workout_start_time) / lubridate::minutes(1)
  )


# distribution
workout_subpop %>%
  dplyr::filter(
    previous_fitness_discipline == "Cycling" 
    & previous_workout_finished == 1
    #& fitness_discipline == "Stretching"
  ) %>% 
  ggplot(mapping = aes(x = num_minutes_between_previous_workout_end_and_current_workout_start, color = fitness_discipline)) + 
  stat_ecdf() + 
  coord_cartesian(xlim = c(0, 15))


```

# at the workout level:
```{r}

# 476,325 total workouts

dat %>%
  dplyr::group_by(
    fitness_discipline
  ) %>%
  dplyr::summarise(num_workouts = dplyr::n_distinct(workout_id)) %>%
  dplyr::arrange(dplyr::desc(num_workouts))

```






# Q2: Which solution- #1 or #2 would you advise the team go with as the first iteration?
* Solution 1: Queue up workout
* Solution 2: Recommend 2-4 classes






```{r}

# 23,717
users %>%
  
  # started at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_started >= 1
  ) %>%
  
  # and started multiple workouts
  dplyr::filter(
    num_total_workouts_started > 1 
  ) %>%
  
  # and finished at least 1 cycling workout
  dplyr::filter(
    num_cycling_workouts_finished >= 1
  ) %>%
  
  dplyr::filter(num_noncycling_workouts_started >= 1)

```




Appproch/Considerations:
* Solution 1: relatively quick back to back classes: people know what they want ahead of time or at least have a specific-ish idea...not spending time browsing and deciding
* Solution 2: don't have a specifhc idea...browsing...and then take it
* Solution 2 requires a recommendation logic, algorithm, engine...use solution 1 to seed solution 2

